Learning by Teaching a Robot:\\The Case of Handwriting

### 2016-01-12 main.tex
[minor] Minor changes suggested by Ferran

Since our application is about teaching a robot to write, generating (initially
bad) letters and learning from demonstrations is a core aspect of the project.

The main insight for both the generation and the learning of letters is to
reason about the shape of letters in their eigenspace, instead of the natural
cartesian space. The eigenspace of each letters is spanned by the first $n$
eigenvectors (in our experiments, $3 < n < 6$) of the covariance matrix
generated from a standard dataset of adult letters (the UJI Pen Characters 2
dataset~\cite{Llorens2008}).  This procedure, based on a Principle Component
Analysis (PCA), is explained in details in a previously published
article~\cite{hood2015when}.

@@

Over the two years of the project, we conducted four studies in schools
(Figure~\ref{fig:schools}). These experiments were meant to technically validate
the system (is it actually able to autonomously write and learn from
demonstrations?) and test the interaction (is the apparatus easy to grasp and to
interact with for children?). We also studied the initial acceptance of the
robot in the school environment (through several formal and informal discussions
with teachers) and how children engage with the robot (and maintain or not this
engagement).

>>>>

Since our application is about teaching a robot to write, generating (initially
bad) letters and learning from writing demonstrations is a core aspect of the
project.

The main insight for both the generation and the learning of letters is to
reason about the shape of letters in their eigenspace, instead of the natural
cartesian space. The eigenspace of each letter is spanned by the first $n$
eigenvectors (in our experiments, $3 < n < 6$) of the covariance matrix
generated from a standard dataset of adult letters (the UJI Pen Characters 2
dataset~\cite{Llorens2008}).  This procedure, based on a Principle Component
Analysis (PCA), is explained in details in a previously published
article~\cite{hood2015when}.

@@

Over the two years of the project, we conducted four studies in schools
(Figure~\ref{fig:schools}). These experiments were meant to technically validate
the system (is it actually able to autonomously write and learn from handwriting
demonstrations?) and test the interaction (is the apparatus easy to grasp and to
interact with for children?). We also studied the initial acceptance of the
robot in the school environment (through several formal and informal discussions
with teachers) and how children engage with the robot (and maintain or not this
engagement).
